---
title: "HomeWork 1"
author: "Sara Hatter"
date: "1/22/2022"
output: pdf_document
---

# Exercise 0

https://github.com/shatter0/Stat-632

# Exercise 1

## (a) Write the equation for the least squares regression line.

$Y_i = \beta_0 + \beta_1 x_i + \epsilon_i$

$Y_i = -1.1016 + 2.2606x + \epsilon_i$

## (b) R performs a t-test whether the slope is significantly different than 0. State the null and alternative hypothesis for this test. Based on the 'p'-value what is the conclusion of the test.

H~0~ = $\beta_1 = 0$ 

H~A~ = $\beta_1 \neq 0$ 

We reject the H_o based on the 'p'-value.


## (c) Calculate the missing 'p'-value for the intercept.

```{r}
2*pt(-2.699, df = 49)
```

## (d) Calculate the missing t-statistic for the slope.

```{r}
(2.2606/0.0981)
```

## (e) Calculate a 95% confidence interval for the slope of the regression line. Does this interval agree with the hypothesis test?

```{r}
qt(0.975, df = 49)

#CI

2.2606 + 2.009575 * 0.0981
2.2606 - 2.009575 * 0.0981

```

Yes, the results from the hypothesis test and confidence interval agreed because zero is not in the critical interval (2.063, 2.458), the null hypothesis is rejected. 

# Exercuse 2

## (a) Show that the least squares estimate of the slope is given 

## (b) Show that 

## (c)


# Exercise 3

## (a)

## (b)

## (c)

## (d)

# Exercise 4

## (a)

## (b)

## (c)

## (d)




